Modelling with ANIMO:\\ between Fuzzy Logic and Differential Equations

### 2015-07-15 Paper.tex
Slightly improved the comparison with the ODE model, and added references to CellNOpt and CytoCopteR

The output of the ANIMO model (see Suppl. Fig.S4) %~\ref{fig:drosophila-model})
matches the original ODE model.
In particular, the oscillations in both models show similar periods and phases (see Fig.~\ref{fig:grafici-drosophila-smaller} for
an example, and Suppl. Fig~S6 %\ref{suppl-fig:grafici-drosophila}
for the complete comparison).
Details of the comparison
between the ANIMO model and the original ODE model are given in Supplementary Section D.3. %~\ref{suppl-sec:animo-drosophila}.

@@

>>>>

The output of the ANIMO model (see Suppl. Fig.S4) %~\ref{fig:drosophila-model})
matches the original ODE model.
In particular, 
both models achieve an oscillatory behaviour with similar periods and phases (see Fig.~\ref{fig:grafici-drosophila-smaller} for
an example, and Suppl. Fig~S6 %\ref{suppl-fig:grafici-drosophila}
for the complete comparison).
Details of the comparison
between the ANIMO model and the original ODE model are given in Supplementary Section D.3. %~\ref{suppl-sec:animo-drosophila}.

@@

As related work, we also signal the powerful tool CellNOpt~\cite{cellnopt}. CellNOpt is a software which can
 work with logic descriptions (Boolean, fuzzy) and differential equations, and automatically suggests
  the best network topologies to match a given data set.
  Thanks to the CytoCopteR plug-in for Cytoscape~\cite{cellnoptr}, which
  provides an accessible user interface,
  CellNOpt can be used in tandem with ANIMO:
  after computing the most likely network topologies with CytoCopteR,
  the biologist can carry on the analysis process with ANIMO, working on 
  new hypotheses to explain the experimental data.
